Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-12-27 ms/manuscript.Rmd
Change randomization method to curveball

Observed values of PD, RPD, FD, RFD, and PE are known to be related to species richness: as more taxa are drawn at random without replacement from a given set, it becomes increasingly unlikely to draw a taxon that is distantly related (or functionally dissimilar) to the others. 
Therefore, we determined whether the observed metrics are more or less diverse than random for a given number of taxa by conducting a randomization test. 
We generated 999 random communities using the "independent swap" algorithm of @Gotelli2000, which conserves richness per site and species occurrence frequencies while randomizing species identities, then compared the observed value to the distribution of random values. 
Statistical significance was assessed using a one-tailed test for PE or a two-tailed test for other metrics with alpha = 0.5; observed values in the extreme 5% of the null distribution were considered significant. 
We also calculated the standard effect size (SES) of each biodiversity metric. 
SES measures how extreme the observed value (*obs*) is relative to the null distribution (*null*):

>>>>

Observed values of PD, RPD, FD, RFD, and PE are known to be related to species richness: as more taxa are drawn at random without replacement from a given set, it becomes increasingly unlikely to draw a taxon that is distantly related (or functionally dissimilar) to the others. 
Therefore, we determined whether the observed metrics are more or less diverse than random for a given number of taxa by conducting a randomization test. 
We generated 999 random communities using the "curveball" algorithm of @Strona2014, which conserves richness per site and species occurrence frequencies while randomizing species identities, then compared the observed value to the distribution of random values. 
Statistical significance was assessed using a one-tailed test for PE or a two-tailed test for other metrics with alpha = 0.5; observed values in the extreme 5% of the null distribution were considered significant. 
We also calculated the standard effect size (SES) of each biodiversity metric. 
SES measures how extreme the observed value (*obs*) is relative to the null distribution (*null*):
